%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Large Colored Title Article
% LaTeX Template
% Version 1.0 (15/8/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{layouts/small_article}

\begin{document}

\input{parts/commands}

\title{Reflection} % Your article title
\author{Nicolas Ganz } % Your name
\date{\today}
\maketitle % Print the title

The whole project was a very interesting experience and I have learned a lot. Artificial Intelligence is and will be a very important part of modern technology and I have now learned the basics and could include this into my programs.

\section*{Summary}
In my opinion was our project a complete success. I have learned a tremendous amount of new information, techniques and technologies. Even though it was a rough time, completing this paper, I really enjoyed the work.

\section*{Teamwork}
The teamwork was all in all very inspiring. Sometimes we were a little lazy, so we got into a hurry at the end but we were both very interested in the topic and worked both hard.\medskip\\
How we worked together was very useful. In our sessions we could help each other, exchange knowledge and with the fixed structure improve our process.

\section*{What Was Positive?}
I really enjoyed the programming parts and I have learned new technologies like Crafty, \LaTeX and of course Artificial Intelligence.\medskip\\
Another interesting aspect was the documentation in English. This way I could improve my English skills.

\section*{What Was Negative?}
We had to write a lot but on the bright side: we really had to know what we are talking about not just what we need to complete our program.\medskip\\
As previously mentioned we both were a little lazy, mainly because it is a very long time and you have to keep on track for the entire time.

\section*{What Could Be Improved?}
The next time we should give us more time and start earlier. This would prevent us from getting into a hurry.

\section*{Future}
In the future I will use AI as much as I can. Maybe I will even study in this area. At least it is sure that I will continue researching and learning about AI and game programming.

\end{document}
