%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Large Colored Title Article
% LaTeX Template
% Version 1.0 (15/8/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\Title{Reflection}
\def\Author{Michael Gerber}
\def\Date{\today}

\input{layouts/small_article}

\begin{document}

\input{parts/commands}

\maketitle % Print the title

Researching, programming and documenting this project finally gave me the opportunity to get to know the field of artificial intelligence. Even though I learned a lot during this time, the project also showed me how much I still don't know. While I now seem to have a firm understanding of how to classify real world problems and how to approach writing algorithms that solve them, how actual consciousness emerges from parts that are themselves unconscious is still a mystery to me.

\section*{Summary}
When working at this project it was hard sometimes to set boundaries and not to dive into every subject that we breached. The field of AI and the implications it has on so many topics is just too extensive to read up on everything. Yet I still consider the project a success since it made me take the time to research things that I always wanted to.

\section*{Teamwork}
In my opinion working together on this project was very constructive. It made us discuss and explain the things we programmed and built in a way that led to a lot of reflection on the matter.\medskip\\
It probably took more time this way, yet it definitely led to a more thorough understanding of the subject.

\section*{What Was Positive?}
The project forced me to finally take some time and read the books that I had been meaning to get for a long time. Writing the game was a lot of fun and posed some interesting and unexpected challenges. Implementing the AI was a great way of using all the theoretical knowledge and actually create something.

\section*{What Was Negative?}
The project required knowledge not just in one area but in at least three. This is the main reason we ran into a little bit of a time shortage and were struggling to meet the deadline without cutting too much of what we were planning to do.

\section*{What Could Be Improved?}
In a project like this one should probably focus on one unfamiliar subject and set clear boundaries from the beginning. Even though we learned a lot in this time, we did have some stressful weeks that could have been avoided.

\section*{Future}
Artificial intelligence is fascinating to me and I will definitely continue to read about the subject, use it in my projects and probably even study it.

\end{document}
