%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Large Colored Title Article
% LaTeX Template
% Version 1.0 (15/8/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{layouts/small_article}

\begin{document}

\input{parts/commands}

\title{Project Journal} % Your article title
\author{Michael Gerber, Nicolas Ganz } % Your name
\date{\today}
\maketitle % Print the title

First of all we worked for the entire project together. Due to this circumstances we decided to create just one project journal.

\section*{Work Process}
We have created the project in different working sessions. They were all structured as followed:
\begin{enumerate}
  \item \textbf{Review:}\\
    What has happened until the last session?\\
    What were the mistakes?
  \item \textbf{Objectives:}\\
    What are necessary objectives of this session?\\
    What would be good to achieve?
  \item \textbf{Coding / writing session:}\\
    Try to reach all defined objectives.
  \item \textbf{Retrospective:}\\
    What did we achieve?\\
    What could we improve the next time?
  \item \textbf{Updating the journal:}\\
    Adding simple steps into the journal
\end{enumerate}

We worked at these locations:
\begin{itemize}
  \item At school
  \item At Starbucks
  \item At home through Skype
  \item At the central library in Zürich
\end{itemize}

\section{Learning about AI}
04.08 - 10.10.2012
\subsection*{Expectations}
It should take a very long time to learn Artificial Intelligence for it is a incredibly large topic. We will continue learning while we work on the other parts of our project. 
\subsection*{Summary}
As we expected it took us very much time to learn AI and we are still unknowing. We learned until we began to write our AI for the game.

\section{Learning \LaTeX}
01.09 - 09.09.2012
\subsection*{Expectations}
We want to learn the markup language \LaTeX to create our documents.
\subsection*{Summary}
\LaTeX is easier than expected. You just have to get the language and just create some documents to get used to it.

\section{Searching a Physics / Game Engine}
09.09 - 10.09.2012
\subsection*{Expectations}
We want to learn about physics and game engines. At the end we hope to find a suitable game engine for our project.
\subsection*{Summary}
Physics and game engines are very interesting but way to complex to learn everything. But we have got a good overview and we have chosen the game engine ``Crafty'' for our project.

\section{Building a Basic Game}
11.09 - 02.10.2012
\subsection*{Expectations}
We think that building a game is very complicated so we just want to build a small, basic one.
\subsection*{Summary}
As expected it was complicated but the engine ``Crafty'' helped us a lot.

\section{Randomizing the World}
27.09 - 03.10.2012
\subsection*{Expectations}
Randomizing the world should not be a big task. But we have to make sure that the generator does not make a unsolvable world.
\subsection*{Summary}
As expected it was not a very complicated task. With some restrictions we build a randomized world and when we restart it creates a new one.

\section{Creating the API}
02.10 - 04.10.2012
\subsection*{Expectations}
We will create an API which triggers keys and checks for the given distance.
\subsection*{Summary}
With this work we have had to go deeper into the game engine because we had to understand how the engine gets triggered and how we can use this for our API. It was very interesting.

\section{Creating a Simple AI}
10.10 - 20.10.2012
\subsection*{Expectations}
While creating a simple AI we should use our theoretical knowledge and see what it really means to create Artificial Intelligence.
\subsection*{Summary}
As expected did we get a taste of the amazing world of AI. We now realize why AI is one of the most respected parts of technology.

\section{Creating a Complex AI}
20.10 - 15.11.2012
\subsection*{Expectations}
We now should have an idea of how to create an AI and should be able to complete the complex AI, including jumping on blocks and using a high performance algorithm.
\subsection*{Summary}
Unfortunately we couldn't create an advanced AI as we planed to. But all in all it works.

\section{Finishing the documents}
15.11 - 20.11.2012
\subsection*{Expectations}
We should:
\begin{itemize}
  \item finish all required documents
  \item compile the \LaTeX code to a PDF
  \item print the PDFs
  \item bind the papers
\end{itemize}
\subsection*{Summary}
We have achieved all requirements above. We had to hurry in the last days but we have could make everything in time.

\end{document}
